# Glossary
*Chapter Preview*. **Loss Data Analytics** contains specific insurance and probability terms which are important to understand the concepts in the book. This glossary can serve as a quick reference when the reader needs to recall a term's definition or location. We also include instructions if the reader wishes to suggest improvements to current definitions.

## Making Changes to Terms and Definitions
When using the glossary, we encourage the reader to provide feedback regarding the terms and their definitions. For example, if the reader feels that there is a better definition for a particular term, the following instructions outline how the reader can suggest improvements.    

* First, open up the issues tab on our repository on GitHub [here](https://github.com/alyaanuval/LDAGlossary/issues).
* Click on "create an issue".
* Indicate which chapters you want to make changes to in the title.
* Specify the terms and definitions you wish to change, add or remove.
* Click "Submit new issue".

## Terms and Definitions by Chapter
Here is a list of important terms and their definitions listed according to the chapters in which they are found.

### Chapter 1 Introduction to Loss Data Analytics

```{r}
library(pander)
chapter1 <- read.csv("~/R project/LDASupplements/csv/Chapter1.csv", header=TRUE,
                       na.strings=c("."), stringsAsFactors=FALSE)
table1.1 <- cbind(chapter1[, 1], chapter1[, 2])
final.table1.1 <- as.data.frame(table1.1)
names(final.table1.1) <- c("Term", "Definition")
pander(final.table1.1)
```

### Chapter 2 Frequency Modeling

```{r}
chapter2 <- read.csv("~/R project/LDASupplements/csv/Chapter2.csv", header=TRUE,
                       na.strings=c("."), stringsAsFactors=FALSE)
table1.2 <- cbind(chapter2[, 1], chapter2[, 2])
final.table1.2 <- as.data.frame(table1.2)
names(final.table1.2) <- c("Term", "Definition")
pander(final.table1.2)
```

### Chapter 5 Aggregate Loss Models

```{r}
chapter5 <- read.csv("~/R project/LDASupplements/csv/Chapter5.csv", header=TRUE,
                       na.strings=c("."), stringsAsFactors=FALSE)
table1.5 <- cbind(chapter5[, 1], chapter5[, 2])
final.table1.5 <- as.data.frame(table1.5)
names(final.table1.5) <- c("Term", "Definition")
pander(final.table1.5)
```
