# Glossary
*Chapter Preview*.

## Making Changes to Terms and Definitions
* First, open up the issues tab on our repository on GitHub [here](https://github.com/alyaanuval/LDAGlossary/issues).
* Click on "create an issue".
* Indicate which chapters you want to make changes to in the title.
* Specify the terms and definitions you wish to change, add or remove.
* Click "Submit new issue".

## Terms and Descriptions by Chapter
Detailed purpose.

### Chapter 1 Introduction to Loss Data Analytics

```{r}
library(pander)
chapter1 <- read.csv("~/R project/LDASupplements/csv/Chapter1.csv", header=TRUE,
                       na.strings=c("."), stringsAsFactors=FALSE)
table1.1 <- cbind(chapter1[, 1], chapter1[, 2])
final.table1.1 <- as.data.frame(table1.1)
names(final.table1.1) <- c("Term", "Description")
pander(final.table1.1)
```

### Chapter 2 Frequency Modeling

```{r}
chapter2 <- read.csv("~/R project/LDASupplements/csv/Chapter2.csv", header=TRUE,
                       na.strings=c("."), stringsAsFactors=FALSE)
table1.2 <- cbind(chapter2[, 1], chapter2[, 2])
final.table1.2 <- as.data.frame(table1.2)
names(final.table1.2) <- c("Term", "Description")
pander(final.table1.2)
```

